Detection of slow slip events using wavelet analysis of GNSS recordings

### 2022-07-06 paper/paper_bssa.tex
Updated submission

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage{color}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{url}

@@

\title{Detection of slow slip events using wavelet analysis of GNSS recordings}
\author[1]{Ariane Ducellier}
\author[2]{Kenneth C. Creager}
\author[2]{David A. Schmidt}
\affil[1]{Corresponding author. University of Washington, Department of Earth and Space Sciences, Box 351310, 4000 15th Avenue NE Seattle, WA 98195-1310}
\affil[2]{University of Washington, Department of Earth and Space Sciences}
\date{}

@@

The GPS recordings used for this analysis can be downloaded from the PANGA website ~\citep{PANGA} \url{http://www.panga.cwu.edu/} and the Geonet website \url{https://www.geonet.org.nz/}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/slowslip}. Figures 3 and 12 were created using GMT ~\citep{WES_1991}.

@@

\bibliographystyle{plainnat}
\bibliography{bibliography}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage{color}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{url}

@@

\title{Detection of slow slip events using wavelet analysis of GNSS recordings}
\author[1]{Ariane Ducellier}
\author[2]{Kenneth C. Creager}
\author[2]{David A. Schmidt}
\affil[1]{Corresponding author. University of Washington, Department of Earth and Space Sciences, Box 351310, 4000 15th Avenue NE Seattle, WA 98195-1310, \href{mailto:ariane.ducellier.pro@gmail.com}{ariane.ducellier.pro@gmail.com}}
\affil[2]{University of Washington, Department of Earth and Space Sciences}
\date{}

@@

The GPS recordings used for this analysis can be downloaded from the PANGA website ~\citep{PANGA} \url{http://www.panga.cwu.edu/} and the Geonet website \url{https://www.geonet.org.nz/}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/slowslip}. Figures 3 and 12 were created using GMT ~\citep{WES_1991}. The Supplementary Material contains three figures showing the effects of boundary conditions, missing data and common modes, and a figure showing four additional small displacements detected in the GPS data.

@@

\bibliographystyle{plainnat_modif}
\bibliography{bibliography}
